---
title: "DDI"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PART FOUR: WHY DO OUR EMPLOYEES LEAVE US?

## Load the library

```{r cars}
library(plyr)
library(dplyr) #filter()
library(corrplot) #corrplot()
library(ggplot2) #ggplot()
library(gridExtra) #grid.arrange()
library(Rmisc) #multiplot()
library(e1071) #naiveBayes()
library(rpart) #raprt()
library(pROC) #roc()
library(rpart.plot) #raprt.plot()
library(randomForest) #randomForest()
library(caret) #confusionMatrix()
library(DT) #datatable()
```

## Understand Data


```{r pressure, echo=FALSE}
hr <- read.csv("HRSurveyData.csv", stringsAsFactors = FALSE)
str(hr)
```

## Data Pre-processing

```{r}
# Rename variables
hr <- rename(hr, satisfaction = satisfaction_level, evaluation = last_evaluation, project = number_project, monthlyhour = average_montly_hours, serviceyear = time_spend_company, accident = Work_accident, promotion = promotion_last_5years, dept = sales)

# Transfer the variable “left” into a factor variable
# hr$left <- factor(hr$left, levels = c("9", "1"))

# Add a new variable salarynum
hr$salarynum[hr$salary == "low"] <-1 
hr$salarynum[hr$salary == "medium"] <-2 
hr$salarynum[hr$salary == "high"] <-3

summary (hr)

```

## Data Analysis and Visualisation: Correlation Matrix
```{r}
hr_cor <- hr %>% select(satisfaction:promotion, salarynum)
corrmatrix <- cor(hr_cor)
corrplot.mixed(corrmatrix)
corrplot(cor(corrmatrix),type="upper",method = "circle",tl.pos = "tl",tl.offset = 0.05)
corrplot(cor(corrmatrix),add=T,type="lower",method = "number",col="red",diag=F, tl.pos ="n",cl.pos ="n")
```

# Transfer variable data type into factor data type
```{r}
hr$accident <- as.factor(hr$accident) 
hr$left <- as.factor(hr$left)
hr$promotion <- as.factor(hr$promotion) 
hr$dept <- as.factor(hr$dept) 
hr$salary <- as.factor(hr$salary)
```

## Analysing categorical variables
```{r}
g1 <- ggplot(group_by(hr, dept), aes(x = dept, fill = dept)) + geom_bar(width =1) +coord_polar(theta = "x") + ggtitle("Chart1: Number of employees in differ ent departments")
g2 <- ggplot(group_by(hr, dept), aes(x = dept, fill = salary)) + geom_bar(width = 1) +
coord_polar(theta = "x") + ggtitle("Chart2: Salary status in different de partments")
multiplot(g1, g2, cols = 2)
```

## Analysing categorical and numerical variables
```{r}
g3 <- ggplot(hr, aes(x = dept, y = satisfaction, fill = dept)) + geom_boxplot()+ggtitle("Chart3: Satisfaction level of different departments") +stat_summary(fun.y = mean,size = 3, color = 'white', geom = "point") + theme(legend.position = "none")

g4 <- ggplot(hr, aes(x = dept, y = evaluation, fill = dept)) + geom_boxplot() +ggtitle("Chart4: Last evaluation of different departments") +
stat_summary(fun.y = mean,size = 3, color = 'white', geom = "point") + theme(legend.position = "none")

grid.arrange(g3, g4, ncol = 2)
```


# Analysing possible reasons of employee attrition
```{r}
ggplot(hr, aes(x = dept, y = evaluation, fill = left)) + geom_boxplot() +
ggtitle("Chart6: Employee attrition status with different last evaluation")
```

```{r}
ggplot(hr, aes(x = dept, y = monthlyhour, fill = left)) + geom_boxplot() +
ggtitle("Chart7: Employee attrition status with different working hours")
```


```{r}
b1 <- ggplot(hr, aes(x = project, fill = left))+geom_bar(position = 'fill' ) +theme_bw() + labs(x = 'numbers of project', y ='percentage')

b2 <- ggplot(hr, aes(x = serviceyear, fill = left)) +geom_bar(position = 'fill')+theme_bw() + labs(x ='years of working in the company’, y =’percentage')

b3 <- ggplot(hr, aes(x = accident, fill = left))+geom_bar(position = 'fill')+theme_bw() + labs(x ='accident since joining the company’， y =‘percenta ge')

b4 <- ggplot(hr, aes(x = promotion, fill = left))+geom_bar(position = 'fill')+theme_bw() + labs(x ='promotion in last 5 years', y = 'percentage')

grid.arrange(b1,b2,b3,b4,ncol = 2, nrow = 2)
```

```{r}
b6<- ggplot(hr, aes(x = salary, fill = left)) + geom_histogram(stat = "count") + ggtitle ("Relat ionship between salary and employee attrition") 

b7 <-ggplot(hr, aes(x = promotion, fill = left)) + geom_histogram(stat = "count") +ggtitle ("Relationship between promot ion in 5 years and employee attrition" ) 

b8 <- ggplot(hr, aes(x = satisfaction, color = left))+ geom_line (stat = "density") + ggtitle ( "Relationship between satisfaction level and employee attrition ") 

b9 <-ggplot(hr, aes(x = evaluation, color = left)) + geom_point (stat = "count") + ggtitle("Relationship between last evaluation and employee attrition " ) 
grid.arrange(b6,b7,b8,b9,ncol = 2,nrow = 2)
```
```{r}
hr %>%
group_by(dept) %>%
ggplot(aes(y = dept,fill = accident)) + geom_bar() + coord_flip() +
theme(axis.text.y = element_blank(), axis.title.y = element_blank(),
axis.title.x = element_blank()) +
scale_fill_discrete(labels = c("no accident", "had accident"))
```

# PART FIVE: MODELING TO PREDICT EMPLOYEE ATTRITION
## Naive Bayes Model
```{r}
set.seed(1234)
n <- nrow(hr)
rnd <- sample(n, n*.70)
train <- hr[rnd,]
test <- hr[-rnd,]
train_control <- trainControl(method = 'cv', number = 5) 
nbmodel <- train(left ~ ., data = train,
trControl = train_control, method = 'nb') 
pred_nb <- predict(nbmodel, test[-7])
```
```{r}
# ROC Curve
pred_nb <- as.numeric(as.character(pred_nb))
roc_nb <- roc(test$left, pred_nb)
Specificity <- roc_nb$specificities
Sensitivity <- roc_nb$sensitivities
ggplot(data = NULL, aes(x = 1- Specificity, y = Sensitivity)) +
geom_line(colour = 'red') + geom_abline() +annotate('text', x =0.4, y =0.5, label = paste ('AUC=', round(roc_nb$auc, 3)))+theme_bw() +
labs(x = '1- Specificity', y = "Sensitivities")
```

```{r}
# Confusion matrix
prop.table(table(pred_nb, test$left, dnn = c("Actual", "Predicted")), 1)
```


## Decision Tree
```{r}
dtree <- rpart(left ~., data = train)
preds <- predict(dtree, test, type = "class")
rocv <- roc(as.numeric(test$left), as.numeric(preds))
rocv$auc
```

```{r}
prop.table(table(test$left, preds, dnn = c("Actual", "Predicted")), 1)
```

```{r}
# Draw he decision tree diagram
rpart.plot(dtree,
type = 4,
extra = 104,
tweak = 0.8,
fallen.leaves = F,
cex = 0.7)
```

# Random Forest
```{r}
index <- sample(2, nrow(hr), replace = T, prob = c(0.7,0.3))
train <- hr[index == 1,]; test <- hr[index == 2,]
rfmodel <- randomForest(left~., data = train)
predict.hr <- predict(rfmodel, test)
```

```{r}
prob.hr <- predict(rfmodel, test, type = "prob")
roc.hr <- roc(test$left, prob.hr[,2], levels = levels(test$left))
plot(roc.hr,type="S", col ="red", main = paste("AUC=", roc.hr$auc, sep = ""))
```

```{r}
confusionMatrix(test$left, predict.hr)
```

## Interative Table of Predicting Employee Attrition
```{r}
predict.hr <- as.numeric(as.character(predict.hr))
pred_end <- predict(rfmodel, test[-7], type = 'prob') 
data_end <- cbind(round(pred_end, 3), predict.hr)
datatable(data_end)
```


